Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-24 krs-survey.tex
Added section on natural language processing

>>>>

The scope of this survey is service robotic, which suggest human-robot
interaction. While numerous modalities of communication between humans and
robots do exist and have been extensively studied, the most challenging of
these interactions is natural, bidirectional, unconstrained verbal
communication. Kruijff et al. provides in~\cite{Kruijff2010} an up-to-date
survey of literature on situated human-robot dialogue, focusing on formal
representation systems, bi-directionality of the interaction and context
building.

Natural Language Processing (NLP) is a large research field by itself, and
while the robotic community may be lagging behind on many theoretical aspects,
it brings one important aspect: the embodiment. Because the interactors, both
the robot and the human, are establishing a communication within a shared
physical context, the verbal communication channel is complemented by deictic
channels, back channels and possibly shared physical experiences: a human can
show something to a robot, saying ``Give me this''. This is simply not possible
for a virtual agent.

Several of the knowledge representation systems we present have developed
specific built-in mechanisms or extensions to parse, ground and possibly
rebuild natural language.
